### 2025-04-18 multiple-regression.qmd
20250417 - clean up figures

car::qqPlot(
  distribution_normal,
  main = "QQ Plot")

@@

car::qqPlot(
  distribution_bimodal,
  main = "QQ Plot")

@@

car::qqPlot(
  distribution_negativeSkew,
  main = "QQ Plot")

@@

car::qqPlot(
  distribution_positiveSkew,
  main = "QQ Plot")

@@

car::qqPlot(
  distribution_lightTailed,
  main = "QQ Plot")

@@

car::qqPlot(
  distribution_heavyTailed,
  main = "QQ Plot")
```

>>>>

car::qqPlot(
  distribution_normal,
  main = "QQ Plot",
  id = FALSE)

@@

car::qqPlot(
  distribution_bimodal,
  main = "QQ Plot",
  id = FALSE)

@@

car::qqPlot(
  distribution_negativeSkew,
  main = "QQ Plot",
  id = FALSE)

@@

car::qqPlot(
  distribution_positiveSkew,
  main = "QQ Plot",
  id = FALSE)

@@

car::qqPlot(
  distribution_lightTailed,
  main = "QQ Plot",
  id = FALSE)

@@

car::qqPlot(
  distribution_heavyTailed,
  main = "QQ Plot",
  id = FALSE)
```
